### 2020-06-12 README.Rmd
readme

<!-- badges: start -->
[![](https://img.shields.io/badge/devel%20version-0.0.0.9600-blue.svg)](https://codecov.io/gh/c1au6i0/covid19census?branch=dev)
[![Travis build status](https://travis-ci.com/c1au6i0/covid19census_dev.svg?token=PM6d4w2yt4HVWw7s2Jgy&branch=dev)
[![Codecov test coverage](https://codecov.io/gh/c1au6i0/covid19census/branch/master/graph/badge.svg)](https://codecov.io/gh/c1au6i0/covid19census?branch=dev)
<!-- badges: end -->

@@

*Note that the package has not been made by, and is not part of the covid19.cesus.gov website.*

>>>>

<!-- badges: start -->
[![](https://img.shields.io/badge/devel%20version-0.0.0.9600-blue.svg)](https://codecov.io/gh/c1au6i0/covid19census?branch=master)
[![Travis build status](https://travis-ci.com/c1au6i0/covid19census_dev.svg?token=PM6d4w2yt4HVWw7s2Jgy&branch=master)
[![Codecov test coverage](https://codecov.io/gh/c1au6i0/covid19census/branch/master/graph/badge.svg)](https://codecov.io/gh/c1au6i0/covid19census?branch=master)
<!-- badges: end -->

@@

*Note that the package has not been made by and is not part of the covid19.census.gov website.*
